---
title: "Data Frames"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include = FALSE}
library(learnr)
```


## 5.1 What is a data frame?

You may remember from the chapter about matrices that all the elements that you put in a matrix should be of the same type. Back then, your data set on Star Wars only contained numeric elements.

When doing a market research survey, however, you often have questions such as:

• ‘Are you married?’ or ‘yes/no’ questions (logical)
• ‘How old are you?’ (numeric)
• ‘What is your opinion on this product?’ or other ‘open-ended’ questions (character)
• . . .

The output, namely the respondents’ answers to the questions formulated above, is a data set of different data types. You will often find yourself working with data sets that contain different data types instead of only one

A data frame has the variables of a data set as columns and the observations as rows. This will be a familiar concept for those coming from different statistical software packages such as SAS or SPSS.

#### Instuctions

Run the code below. The data from the built-in data frame mtcars will be printed.

```{r exercise 5.1, exercise = TRUE}
# Print out built-in R data frame
mtcars
```

## 5.2 Quick, have a look at your data set

Wow, that is a lot of cars!

Working with large data sets is not uncommon in data analysis. When you work with data sets and data frames, your first task as a data analyst is to develop a clear understanding of its structure and main elements. Therefore, it is often useful to show only a small part of the entire data set.

So how to do this in R? Well, the function head() enables you to show the first observations of a data frame. Similarly, the function tail() prints out the last observations in your data set. 

Both head() and tail() print a top line called the ‘header’, which contains the names of the different variables in your data set.

#### Instructions

Call head() on the mtcars data set to have a look at the header and the first observations.

```{r exercise 5.2, exercise = TRUE}
# Call head() on mtcars


#
```

```{r exercise 5.2-solution}
# Call head() on mtcars
head(mtcars)

#
```

## 5.3 Have a look at the structure

Another method that is often used to get a rapid overview of your data is the function str(). The function str() shows you the structure of your data set. For a data frame it tells you:

• The total number of observations (e.g. 32 car types)
• The total number of variables (e.g. 11 car features)
• A full list of the variables names (e.g. mpg, cyl . . . )
• The data type of each variable (e.g. num)
• The first observations

Applying the str() function will often be the first thing that you do when receiving a new data set or data frame. It is a great way to get more insight in your data set before diving into the real analysis.

####Instructions

Investigate the structure of mtcars. Make sure that you see the same numbers, variables and data types as mentioned above.

```{r exercise 5.3, exercise = TRUE}
# Investigate the structure of mtcars


#
```

```{r exercise 5.3-solution}
# Investigate the structure of mtcars
str(mtcars)

#
```

































































































